\huge A Usability Evaluation of Tor Launcher

### 2016-11-10 pets2017-paper/pets2017-paper.tex
add in the interface screenshots

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{adjustbox}
%\usepackage{hyperref}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
\caption{
A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
}
\label{fig:old-interface}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
\caption{
A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
}
\label{fig:new-interface}
\end{figure*}

>>>>

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{adjustbox}
\usepackage{subcaption}
%\usepackage{hyperref}

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
	\label{fig:old-bridge}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\caption{Instructions on getting a custom bridge.Clicking the ``Help'' button in Figures~\ref{fig:old-bridge settings} and \ref {fig:old-bridge-combobox} leads to this page.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
	\label{fig:old-proxy}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\caption{Where users fill in proxy information.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\caption{The progress bar.}
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored enviroinments.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
	\label{fig:new-proxy}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\caption{There is only one bridge screen now. The default is to connect without one.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
	\label{fig:new-bridge}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\caption{The transports selections are the same.}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\caption{These instuctions are also the same.}
	\label{fig:new-bridge-help}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}
